---
title: "Project 3: STAT302package Tutorial"
author: "Anna Vasyura"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STAT302package)
```

## Introduction

This R package contains several functions written for STAT302 at the University of Washington in Spring 2021. Those functions include `my_t.test`, `my_lm`, `my_knn_cv`, and `my_rf_cv`. You can use them for running a t test, creating a linear model, or cross-validation with k-nearest neighbors or random forest. The package can be installed from GitHub using the following code:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("anna-vasyura/STAT302package")
library(STAT302package)
```

## Tutorial for my_t.test

x <- as.vector(subset(data.frame(my_gapminder), select = c("lifeExp")))
alternative <- c("two.sided", "less", "greater")
mu <- 60

my_t.test(x, alternative = "two.sided", mu)

my_t.test(x, alternative = "less", mu)

my_t.test(x, alternative = "greater", mu)

## Tutorial for my_lm

## Tutorial for my_knn_cv

## Tutorial for my_rf_cv